Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-23 writing/embedded_meta_learning_appendix.tex
Further tweaks

\section{Clarifying meta-mappings} \label{app_clarifying_meta_mapping}

@@

\item There are also truly held-out tasks that the system has never seen in training. These are the held-out tasks that we evaluate on at the end of training and report results.

@@

This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization. There are also meta-mappings which have never been encountered during training, and those are the meta-mappings we evaluate on at hte end of training. We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.

>>>>

\section{Clarifying meta-mapping} \label{app_clarifying_meta_mapping}

@@

\item There are also truly held-out tasks that the system has never seen in training. These are the held-out tasks that we evaluate on at the end of training and that are plotted in the ``Held out'' sections in the main plots.

@@

This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization. There are also meta-mappings which have never been encountered during training, which we evaluate on at the end of training, those are the meta-mappings which are plotted in the ``held out'' section in the relevant plots. We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained. \par
